---
title: "HW6"
author: "Maiko Hata and Michelle Cui"
date: "2024-11-06"
format: pdf
execute:
  eval: true
  echo: false
fig-width: 6.5
fig-height: 8
bibliography: biblio.bib
---

```{r}
#| echo: false
#| include: false
library(tidyverse)
library(here)
library(rio)
library(knitr)
library(gt)
library(DT)
library(reactable)
library(gtsummary)
library(kableExtra)
```
<<<<<<< Updated upstream
=======

```{r}



```
>>>>>>> Stashed changes

# What is Intersectionality and why is it important?

@crenshaw1987theories emphasized the importance of intersectionality as a research framework, stating that “Because the intersectional experience is greater than the sum of racism and sexism, any analysis that does not take intersectionality into account cannot sufficiently address the particular manner in which Black women are subordinated” (p. 140)." Studies show that this stands true as studies show that infants and toddlers of color are underrepresented in Early Intervention (EI) services [see @cycyk2022moving; @cho2005korean; @cycyk2020supporting].


# Table 1
```{r}
#| results: asis
#| message: false
star_df <- import(here("Data","star.csv"))

star_df %>% 
  characterize() %>% 
  group_by(sex,frl) %>% 
  summarize(math_mean = round(mean(tmathss, na.rm = T), digits = 2),
            math_sd = round(sd(tmathss, na.rm = T), digits = 2),
            rdg_mean = round(mean(treadss, na.rm = T), digits = 2),
            rdg_sd = round(sd(treadss, na.rm = T), digits = 2)) %>% 
  kable()

```

Description: As it is presented in the Table 1, both boys and girls in the no free/reduced lunch group has higher average standardized scores than the boys and girls in the free lunch group. In addition, in the free lunch group, the boys' average standardized score is lower than that of the girls'. It seems the both household income and gender influence the students reading and math performance.

# Plot 1 Relationship between teacher experience and math scores
```{r}
#|warning: False
#|message: false
star_df %>% 
  ggplot(aes(totexp, tmathss, color = frl)) +
  geom_point(color = "grey") +
  geom_smooth(formula = y ~ x, method = 'lm')+
  labs(title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced price lunch status",
       x = "Teacher Experience (years)",
       y = "Total Math Scale Score")+
  theme_minimal() +
  guides(color = guide_legend(title = "Lunch status",
                              position = "bottom"))+
  scale_colour_discrete(breaks = c("yes","no"),
                        labels = c("Free/Reduced Price Meals", "Paid Meals"))

```


\newpage

# References

